---
title: "Get mail list"
author: "AJ Perez-Luque (@ajpelu); M Suarez-Munoz"
date: "2016 March"
output:  
    md_document:
      variant: markdown_github
---

### Create a csv with the potential mail list 

We compiled a mail list from several sources: 

* Dossier
* Sierra Nevada LTER Research community
* Literature Review Search (WOS)

#### Dossier
A sql query to db `dossier_filiaciones` was done

```{r, engine='sql', eval=FALSE}
SELECT 
  dicc_autores.email
FROM 
  public.dicc_autores;
```

Save as: `/data/mail_raw/dossier_filiaciones.csv`

#### Sierra Nevada LTER Research community

Several sql queries from db `nodo_lter_sn`

```{r, engine='sql', eval=FALSE}
SELECT 
  "Investigadores_solicitudes".email
FROM 
  public."Investigadores_solicitudes" 
WHERE 
  "Investigadores_solicitudes".email IS NOT NULL AND
  "Investigadores_solicitudes".email <> '';
``` 

Save as: `/data/mail_raw/investigadores_solicitudes.csv`

```{r, engine='sql', eval=FALSE}
SELECT 
  eez.email
FROM 
  public.eez
WHERE 
  eez.email IS NOT NULL AND
  eez.email <> '';
```

Save as: `/data/mail_raw/eez.csv`

#### Literature Review Search (WOS)
Get the data from [`/analysis/cleaning_data.md`](analysis/cleaning_data.md)


## Read all data and create output mailist 



```{r wd, echo=FALSE}
#---------------------------------
# Set working directory 
machine <- "/Users/ajpelu"
# machine <- "/Users/ajpeluLap"

di <- paste(machine, "/Dropbox/Review_Sierra_Nevada/sngc_review", sep = "")
#---------------------------------
```

```{r packages}
library("dplyr")
```

```{r}
# Read data
mail_wos <- read.csv(file=paste(di, "/data/output/lista_emails_wos.csv", sep=""),
                     header=TRUE) 

mail_dos <- read.csv(file=paste(di, "/data/mail_raw/dossier_filiaciones.csv", sep=""), 
                     header=TRUE) 

mail_inv <- read.csv(file=paste(di, "/data/mail_raw/investigadores_solicitudes.csv", sep=""), 
                     header=TRUE) 
    
mail_eez <- read.csv(file=paste(di, "/data/mail_raw/eez.csv", sep=""), 
                     header=TRUE) 

# Join, remove duplicates and sort 
mail <- rbind_all(list(mail_eez,mail_inv,mail_dos,mail_wos)) %>%
  unique() %>%
  arrange(email) 

# Export 
write.csv(mail, file=paste(di, "/data/output/potential_mail.csv", sep=""), quote=FALSE, row.names = FALSE)
```
